\newpage
\section{Resumé}

The purpose of the project is to develop a webshop for the electronics goods store Elektroshoppen. Elektroshoppen owns 40 stores country wide, and is in need of a centralized system, that can help them bring in more customers, and give a boost to their earnings.
The development process, Unified process were used to build the product, and help determine the ideas behind the project through Use cases. unified process is split into 4 phases: Inception, elaboration, construction and transition. Inception phase is where the ideas of the project start taking shape. The base for the project is developed by identifying common use cases from users, and how the system should react to the user inputs. This first phase develops a black box structure of the program.

In the elaboration phase, the developmenet of the system starts. where the models from the inception Phase turns into code, throuugh analyses and design. at the end of the elaboration phase we have a barebone program that just needs filling through the next phase: the Construction phase.

In the construction phase all the functionality is created, and at the end there should be an almost complete program. Last phase is transaction where the program is prepared for the customers to start using the program. Each phase have a number of iterations that it runs through in order to get a finished produkt. look at figure \ref{fig:UPFaser} on page \pageref{fig:UPFaser}
In this project, the goal is to prepare the program for the construction phase in the best way possible.

This report only covers the first 2  fases of the projekt, inception and elaboration.